Discovery of s-process stars in the LAMOST survey

### 2018-02-06 article/ms.tex
add seln fun things

\subsubsection{Abundance analysis}
We adopted the stellar parameters ($T_{\rm eff}$, $\log_{10}g$, [Fe/H]) provided from the data-driven analysis of \citep{ho2017}. Following the procedure outlined in \citep{casey2014}, we measured the strength of \ion{Ba}{II} (4554\,\AA, 4934\,\AA, and 6496\,\AA) and \ion{Sr}{II} (4077\,\AA\ and 4215\,\AA) absorption lines by spectral synthesis, using s-process isotopic ratios from \citet{sneden08}. The abundance ratios we estimate from high-resolution spectra are in excellent agreement with our estimates from LAMOST spectra, all agreeing within the joint $1.2\sigma$. Specifically, for J09162834+02593480 from high- and low-resolution spectra, respectively, we find $[{\rm Sr/Fe}] = 0.76 \pm 0.10$ and $0.85 \pm 0.21$, and $[{\rm Ba/Fe}] = 0.92 \pm 0.10$ and $0.77 \pm 0.21$. The biggest discrepancy we find between high- and low-resolution spectra is [Sr/Fe] for J09162834+0259348, where we find $[{\rm Sr/Fe}] = 0.62 \pm 0.07$ and $0.90 \pm 0.22$ from Magellan/MIKE and LAMOST, respectively. Finally, for J09162834+0259348 we find $[{\rm Ba/Fe}] = 0.94 \pm 0.12$ from high-resolution spectra and $[{\rm Ba/Fe}] = 0.80 \pm 0.26$ from low-resolution spectra. Uncertainties on abundances derived from high-resolution spectra are taken as the standard deviation of multiple line measurements.

@@

\subsection{Dynamics}
We integrated galactic orbits for 21 Barium stars using recent astrometry from Gaia/TGAS \citep{gaia2016a,gaia2016b}. Using the \texttt{gala} Python package, we integrated each star backwards for $0.5\,\textrm{Gyr}$ in a Milky Way-like potential that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo. In this potential, the disk and bulge parameters were adjusted to be consistent with previous work \citep{bovy2015}, and to vary the scale mass and radius, of the nucleus and halo, respectively. We computed orbital periods, energy, apocenters, pericenters, eccentricities, and angular momentum in the $z$-direction. All 21 stars showed prograde orbits that were consistent with membership in the Milky Way disk.

@@

\subsection{Extrinsic and intrinsic Barium stars}
Barium stars exist as either intrinsic or extrinsic objects. Intrinsic Barium stars must be massive enough to reach the TP-AGB phase, and extrinsic Barium stars must be in a binary with a previously polluting TP-AGB star companion. Figure \ref{fig:figure2} shows that the majority of our Barium stars have $\log{g} > 2$, highlighting that most stars in our sample are not massive enough to have already reached the TP-AGB phase and therefore, must be extrinsic Barium stars. The classification for Barium stars with $\log{g} < 2$ is uncertain: these stars could be intrinsic or extrinsic. From here on when we refer to extrinsic Barium stars, we specifically refer to those with $\log{g} > 2$. It is noted, in the previous literature \citet{van2017}, only 22\% of their stellar sample are post-main-sequence barium stars (extrinsic barium stars). In comparison, we find our Barium candidates constitute greater than 70\% extrinsic, this suggests the construction of our data-driven model may have missed some AGB Barium candidates, or that previous studies were biased towards finding luminous intrinsic AGB Barium stars.

@@

\section*{Acknowledgements}
We thank Alex Ji (Carnegie Observatories) for useful discussions.
A.~R.~C. is supported through an Australian Research Council Discovery Project under grant DP160100637.
A.~Y.~Q.~H. is supported by a Fulbright grant through the German-American Fulbright Commission and a National Science Foundation Graduate Research Fellowship under Grant No. DGE-1144469. 
This research has made use of NASA's Astrophysics Data System.
Guoshoujing Telescope (the Large Sky Area Multi-Object Fiber Spectroscopic Telescope LAMOST) is a National Major Scientific Project built by the Chinese Academy of Sciences. Funding for the project has been provided by the National Development and Reform Commission. LAMOST is operated and managed by the National Astronomical Observatories, Chinese Academy of Sciences.

>>>>

\subsubsection{Abundance analysis}
We adopted the stellar parameters ($T_{\rm eff}$, $\log_{10}g$, [Fe/H]) provided from the data-driven analysis of \citep{ho2017}. Following the procedure outlined in \citep{casey2014}, we measured the strength of \ion{Ba}{II} (4554\,\AA, 4934\,\AA, and 6496\,\AA) and \ion{Sr}{II} (4077\,\AA\ and 4215\,\AA) absorption lines by spectral synthesis, using s-process isotopic ratios from \citet{sneden08}. The abundance ratios we estimate from high-resolution spectra are in excellent agreement with our estimates from LAMOST spectra, all agreeing within the joint $1.2\sigma$. Specifically, for J09162834+02593480 from high- and low-resolution spectra, respectively, we find $[{\rm Sr/Fe}] = 0.76 \pm 0.10$ and $0.85 \pm 0.21$, and $[{\rm Ba/Fe}] = 0.92 \pm 0.10$ and $0.77 \pm 0.21$. The biggest discrepancy we find between high- and low-resolution spectra is [Sr/Fe] for J09162834+0259348, where we find $[{\rm Sr/Fe}] = 0.62 \pm 0.07$ from our Magellan/MIKE spectra, and $0.90 \pm 0.22$ from LAMOST. Finally, for J09162834+0259348 we find $[{\rm Ba/Fe}] = 0.94 \pm 0.12$ from high-resolution spectra and $[{\rm Ba/Fe}] = 0.80 \pm 0.26$ from low-resolution spectra. Uncertainties on abundances derived from high-resolution spectra are taken as the standard deviation of multiple line measurements. The high-resolution abundances we find help validate our methodology for candidate selection, and for estimating abundances from LAMOST spectra.

@@

\subsection{Dynamics}
We integrated galactic orbits for 21 Barium stars using recent astrometry from Gaia/TGAS \citep{gaia2016a,gaia2016b}. Using the \texttt{gala} Python package \citep{price2017}, we integrated each star backwards for $0.5\,\textrm{Gyr}$ in a Milky Way-like potential that consists of four components: a \citet{hernquist1990} bulge and nucleus, a \citet{miyamoto1975} disk, and the \citet{nfw1997} halo. In this potential, the disk and bulge parameters were adjusted to be consistent with previous work \citep{bovy2015}, and to vary the scale mass and radius, of the nucleus and halo, respectively. We computed orbital periods, energy, apocenters, pericenters, eccentricities, and angular momentum in the $z$-direction. All 21 stars showed prograde orbits that were consistent with membership in the Milky Way disk.

@@

\subsection{Extrinsic and intrinsic Barium stars}
Barium stars exist as either intrinsic or extrinsic objects. Intrinsic Barium stars must be massive enough to reach the TP-AGB phase, and extrinsic Barium stars must be in a binary with a previously polluting TP-AGB star companion. Figure \ref{fig:figure2} shows that the majority of our Barium stars have $\log{g} > 2$, highlighting that most stars in our sample are not massive enough to have already reached the TP-AGB phase and therefore, must be extrinsic Barium stars. The classification for Barium stars with $\log{g} < 2$ is uncertain: these stars could be intrinsic or extrinsic. From here on when we refer to extrinsic Barium stars, we specifically refer to those with $\log{g} > 2$. It is noted, in the previous literature \citet{van2017}, only 22\% of their stellar sample are post-main-sequence barium stars (extrinsic barium stars). In comparison, we find our Barium candidates constitute greater than 70\% extrinsic, this suggests the construction of our data-driven model may have missed some AGB Barium candidates, or that previous studies were biased towards finding luminous intrinsic AGB Barium stars. Given that our analysis limits us to only giant stars, such that we do not find any extrinsic Barium stars on the main-sequence, na\"ively we would expect that our sample would be biased \emph{towards} finding a higher fraction of intrinsic AGB Barium stars. Despite this expected bias against extrinsic Barium stars, fully 70\% of our sample are extrinsic Barium stars, suggesting unaccounted selection biases in previous studies towards luminous intrinsic Barium stars.

@@

\section*{Acknowledgements}
We thank Alex Ji (Carnegie Observatories) for useful discussions.
A.~R.~C. is supported through an Australian Research Council Discovery Project under grant DP160100637.
A.~Y.~Q.~H. is supported by a Fulbright grant through the German-American Fulbright Commission and a National Science Foundation Graduate Research Fellowship under Grant No. DGE-1144469. 
This research has made use of NASA's Astrophysics Data System.
Guoshoujing Telescope (the Large Sky Area Multi-Object Fiber Spectroscopic Telescope LAMOST) is a National Major Scientific Project built by the Chinese Academy of Sciences. Funding for the project has been provided by the National Development and Reform Commission. LAMOST is operated and managed by the National Astronomical Observatories, Chinese Academy of Sciences. 
This work has made use of data from the European Space Agency (ESA) mission Gaia (http://www.cosmos.esa.int/gaia), processed by the Gaia Data Processing and Analysis Consortium (DPAC, http://www.cosmos.esa.int/web/gaia/dpac/consortium). Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the Gaia Multilateral Agreement.
